The Galactic Midplane is Not a Plane: Implications for dynamical analysis with {\em Gaia} data and beyond

### 2019-04-22 paper/ms.tex
Add bit more about galactocent. in intro

Underlying the quantitative analysis of many of the mechanisms at work that
give rise to these signatures is the assumption of a global, axisymmetric
Galactocentric coordinate system \citep{2008gady.book.....B} in which the
Sun's position (and therefore the origin of the coordinate system) can be
defined and measured both precisely and accurately.

>>>>

Underlying the quantitative analysis of many of the mechanisms at work that
give rise to these signatures is the assumption of a global, axisymmetric
Galactocentric coordinate system \citep{2008gady.book.....B} in which the
Sun's position (and therefore the origin of the coordinate system) can be
defined and measured both precisely and accurately. This involves measuring
the Galactic center, the orientation of the Galactic plane, the distance from
the Sun to the Galactic center, the height of the Sun above the Galactic
midplane, and the local standard of rest (LSR). We discuss the observational
efforts to measure all these parameters in Section~\ref{sec:mes_err}.
